A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-02-14 paper/paper1/ms.tex
anticipating a merge conflict

\subsection{Cause for stellar modulation}
The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days, and with some sectors exhibiting lower amplitudes of modulation.  The baseline interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.  The cause for such orbital and rotational synchronization would then ostensibly be tides.  We examine the prospect of tides in the next subsection.

Instead, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of star-planet-interaction (SPI) that we consider now.  In this scenario, the magnetic field of the planet permeates the space between the star and planet.  Magnetic perturbations propagate via planetary magnetic fields with the Alfv\'en speed.  The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controling the bulk motion of intervening medium.  The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down motion entirely.  \citet{2011ApJ...738....1B} estimate this range as between about 1-30 Gauss.  With

>>>>

\subsection{Cause for stellar modulation}
The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days. Some sectors exhibit lower amplitudes.  The conventional interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.  The cause for such orbital and rotational synchronization would then ostensibly be tides.  We examine the prospect of tides in the next subsection.

Alternatively, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of Star Planet Magnetic Interaction (SPMI) that we consider now.  In this scenario, the magnetic field of the planet permeates the space between the star and planet.  Magnetic perturbations propagate via planetary magnetic fields with the Alfv\'en speed.  The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controling the bulk motion of intervening medium.  The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down charged particle motion entirely.  \citet{2011ApJ...738....1B} estimate this range as between about 1-30~G.
